### 2019-08-02 README.Rmd
updated vignette/website compilation
fix link in readme

``` r
devtools::install_github("richarddmorey/Morey_Hoekstra_StatCognition")
```

@@

You can find an [online version of the task demonstration](articles/task_demo.html).

>>>>

``` r
devtools::install_github("richarddmorey/Morey_Hoekstra_StatCognition", build_vignettes = TRUE, depedencies = TRUE)
```

@@

You can find an [online version of the task demonstration](https://richarddmorey.github.io/Morey_Hoekstra_StatCognition/articles/task_demo.html).
